Towards Verifying the Bitcoin-S Library

### 2019-06-20 paper/paper.tex
removed BasicArithmetic

extracted 3 classes (they are in code/addition/src/main/scala/addition/original)

@@

  - removed extending Factory and NetworkElement abstract class. This includes some hex/byte conversion eg fromHex, hex, bytes, fromBytes, ...
    \href{https://bitcoin-s.org/docs/core/core-intro\#the-basics}{description in section \#the-basics (cannot add link with hashtag)}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/protocol/NetworkElement.scala}{NetworkElement class}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/util/Factory.scala}{Factory class}

@@

Here we can see the extracted code needed for the addition of CurrencyUnits:
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/number/BasicArithmetic.scala}
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/number/NumberType.scala}
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/currency/CurrencyUnits.scala}

>>>>

extracted 2 files (they are in code/addition/src/main/scala/addition/original)

@@

  - removed extending Factory, NetworkElement and BasicArithmetic. This includes some hex/byte conversion eg fromHex, hex, bytes, fromBytes, ... Just interfaces never referenced
    \href{https://bitcoin-s.org/docs/core/core-intro\#the-basics}{description in section \#the-basics (cannot add link with hashtag)}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/protocol/NetworkElement.scala}{NetworkElement class}
    \href{https://github.com/bitcoin-s/bitcoin-s/blob/master/core/src/main/scala/org/bitcoins/core/util/Factory.scala}{Factory class}

@@

Here we can see the extracted code needed for the addition of CurrencyUnits:
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/number/NumberType.scala}
\lstinputlisting[language=scala]{../code/addition/src/main/scala/addition/reduced/currency/CurrencyUnits.scala}
